Overview

### 2019-03-15 notebooks/general_info.Rmd
added function to display data frames in notebook, and functions to get fully monomorphic things (i.e., monomorphic in class, attribue, and type). the counts are available in the notebook, just not being printed yet (you might need to open it with RStudio to see)

```{r, echo=FALSE}
source("../code/data_processing.R")

los <- list.files("../data/full_sigs", full.names=TRUE)
names <- list.files("../data/full_sigs")
names(los) <- substr(names, 1, nchar(names)-4)
los <- lapply(los, readRDS)
los <- remove_empties(los)
# annoying strange error that I should fix pops up
```

@@

Then, pick out the ones you want.
```{r}
print_me <- head(poly_type_args, 20)
print_me$type <- sapply(print_me$type, function(x) paste0(x[[1]], collapse=", "))
print_me
# I need to streamline this, too many weird lists appearing...
```

@@

Printing is as before.
Note that ATM I also have attribute type information in here.
I'll get it to display just the names as well.
I figured this might be interesting, and I don't expect many functions to be polymorphic in this way.
```{r}
# will fix printing, its annoying atm
print_me_a <- head(poly_attr_args, 20)
print_me_a$attr <- sapply(print_me_a$attr, function(x) paste0(x[[1]], collapse=", "))
print_me_a
```

```{r}
print_me_c <- head(poly_class_args, 20)
print_me_c$class <- sapply(print_me_c$class, function(x) paste0(x[[1]], collapse=", "))
print_me_c
```

>>>>

```{r}
source("../code/data_processing.R") # get the functions we need
```

```{r, echo=FALSE}
los <- list.files("../data/full_sigs", full.names=TRUE)
names <- list.files("../data/full_sigs")
names(los) <- substr(names, 1, nchar(names)-4)
los <- lapply(los, readRDS)
los <- remove_empties(los)
# annoying strange error that I should fix pops up
```

@@

Then, pick out the ones you want.
The `format_df_for_print` function is just for letting the notebook display the data frame properly.
The type, attr, and class rows are lists of lists.
```{r}
format_df_for_print(poly_type_args[1:20,])
```

@@

Printing is as before.
Note that ATM I also have attribute type information in here.
I'll get it to display just the names as well.
I figured this might be interesting, and I don't expect many functions to be polymorphic in this way.
```{r}
format_df_for_print(poly_attr_args[1:20,])
```

```{r}
format_df_for_print(poly_class_args[1:20,])
```
